BeeModeling

### 2022-07-27 Fowler-GLOBI Modeling/GLOBI-Fowler Data Prep-reformatted.Rmd
update plant names using the plant list

library(lifecycle)
library(rvest)
library(dplyr)
library(plotly)
library(tidyverse)
library(data.table)

@@

Let's do some reformatting
```{r}
capitalize = function(a_string){

@@

globi_summ = interactions_b %>% 
  mutate(scientificName = capitalize(sourceTaxonSpeciesName), 
         plant_family = capitalize(targetTaxonFamilyName), 
         plant_genus = capitalize(targetTaxonGenusName)) %>%
  filter(scientificName != '' & plant_family !='' & plant_genus != "") %>% 
  group_by(scientificName, plant_genus, plant_family,) %>% 
  summarize(n_genus = n()) %>% ungroup()

@@

#calculate the number of plant genera each bee species is observed visiting
degree_by_genus = globi_summ %>%
  left_join(total_obs) %>%
  mutate(freq_squared = (n_genus/n)^2) %>% 
  group_by(scientificName) %>%
  summarize(degree_genus = n_distinct(plant_genus), 
            degree5_genus = sum(n_genus >= 5), weighted_degree_genus = sum(freq_squared))

globi_degree = degree_by_fam %>% left_join(degree_by_genus) %>%
  mutate(diet_breadth = ifelse(scientificName %in% specialists,'specialist','generalist'))

# write_csv(globi_degree,'modeling_data/globi_degree.csv')

>>>>

library(lifecycle)
library(rvest)
library(dplyr)
library(plotly)
library(tidyverse)
library(data.table)
library(readxl)
library(Taxonstand)

@@

Let's reformat and update the plant names in the interaction data 
```{r}
capitalize = function(a_string){

@@

interactions_reformat = interactions_b %>% 
  mutate(scientificName = capitalize(sourceTaxonSpeciesName), 
         bee_family = capitalize(sourceTaxonFamilyName),
         plant_family = capitalize(targetTaxonFamilyName), 
         plant_genus = capitalize(targetTaxonGenusName),
         plant_species = capitalize(targetTaxonName)) %>%
  filter(scientificName != '' & plant_family !='' & plant_genus != "")

#

plant_df = interactions_reformat %>%
  distinct(plant_species)
test_me = plant_df$plant_species

# check_names = TPL(test_me) #takes forever to run, download output as csv
# write_csv(check_names,'modeling_data/plant_list_name_update.csv')
check_names = read_csv('modeling_data/plant_list_name_update.csv')

check_names %>% filter(Taxonomic.status != 'Accepted') %>% 
  select(Taxon,New.Genus,New.Species)

tpl_formatted = check_names %>% rename(plant_species = Taxon) %>% 
  mutate(accepted_name = ifelse(!is.na(New.Species),paste(New.Genus,New.Species),New.Genus) ) %>%
  mutate(accepted_name = ifelse(is.na(accepted_name), plant_species, accepted_name)) %>%
  select(plant_species,accepted_name)

tpl_formatted %>% filter(is.na(accepted_name))

#add accepted_name column to plant_df
interactions_updated = interactions_reformat %>% 
  group_by(scientificName,bee_family,plant_species,plant_family) %>%
  summarize(n=n()) %>%
  ungroup %>%
  left_join(tpl_formatted) %>%
  select(-plant_species) %>%
  rename(plant_species = accepted_name) %>%
  mutate(plant_genus = sub(" .*","",plant_species))

Let's do some reformatting
```{r}

globi_summ = interactions_updated %>%
  group_by(scientificName, plant_genus, plant_family,bee_family) %>%
  summarize(n_genus = sum(n)) %>% ungroup()

@@

#calculate the number of plant genera each bee species is observed visiting
degree_by_genus = globi_summ %>%
  left_join(total_obs) %>%
  mutate(freq_squared = (n_genus/n)^2) %>% 
  group_by(scientificName,bee_family) %>%
  summarize(degree_genus = n_distinct(plant_genus), 
            degree5_genus = sum(n_genus >= 5), weighted_degree_genus = sum(freq_squared))

globi_degree = degree_by_fam %>% left_join(degree_by_genus) %>%
  mutate(diet_breadth = ifelse(scientificName %in% specialists,'specialist','generalist'))
getwd()
# write_csv(globi_degree,'modelign_data/globi_degree.csv')
